---
title: "HW5"
author: "Soham Ghose"
date: "May 6, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
```

1)	Consider the following regression and output in R.  The data here is the reshaped data where we're only looking at the Tropicana sales.  Features include price of Dominicks, MM and Trop, though, and feat is only for Tropicana being featured.
a.	What is the expected change in quantity (in percents) for a 10% increase in the price of Trop?

Decrease by 23%

b.	What is the expected change in quantity (in percents) for a 10% increase in the price of MM?

Increase by 2.65%

c.	Why should we be concerned about inferring causality from the coefficient on log(P_Trop):feat?

A brand may only be featured if the company decides to lower the price. If this is the case, then the change in quantity will be attributed to the lower price and not necessarily to the fact that it was featured, which makes the causality hard to interpret.  

d.	If Trop is a normal good, what would you expect the sign of the interaction of INCOME and log(P_Trop) to be?
Positive. Income has a positive correlation with quantity demanded. So when Income goes up, price elasticity should be closer to 0.  

```{r oj, echo=TRUE}
OJ <- read.csv("oj.csv")
OJ$logp <- log(OJ$price)
Df1 <- OJ
Df1$week <- Df1$week+1

Df2 <- merge(OJ, Df1, by=c("brand","store","week"))

Df2 <- Df2 %>% 
  rename(
    lastweekprice = price.x ,
    lastweeklogp = logp.x,
    lastweekfeat = feat.x, 
    logmove= logmove.y, 
    logp= logp.y,
    feat = feat.y , 
    EDUC = EDUC.y, 
    INCOME = INCOME.y, 
    ETHNIC = ETHNIC.y , 
    AGE60 = AGE60.y , 
    HHLARGE = HHLARGE.y
  )
OJnew <- Df2 %>%  select( brand , store , logp, week) %>% 
  spread(brand, logp) 

Df3 <- Df2 %>% select(brand, store, logmove.x, logmove, week , logp, feat, lastweeklogp,HVAL150.y ,  SSTRDIST.y , SSTRVOL.y ,CPDIST5.y, CPWVOL5.y,
                      INCOME, EDUC, HHLARGE,  AGE60, WORKWOM.y, ETHNIC)

OJ2 <- full_join(OJnew , Df3, by = c("store","week")) 

dominicks <- OJ2 %>% filter(brand == "dominicks")

summary(dominicks$INCOME)

IncomeQ1 <- dominicks %>% filter(INCOME <= 10.456)
IncomeQ2 <- dominicks %>% filter(between(INCOME, 10.456, 10.635))
IncomeQ3 <- dominicks %>% filter(between(INCOME, 10.635, 10.797))
IncomeQ4 <- dominicks %>% filter(INCOME > 10.797)
```
#Means within each quartile

```{r oj2, echo=TRUE}
m1 <- mean(IncomeQ1$logmove)
m2 <- mean(IncomeQ2$logmove)
m3 <- mean(IncomeQ3$logmove)
m4 <- mean(IncomeQ4$logmove)

m1
m2
m3
m4

```

SST withing each quartile
```{r oj3, echo=TRUE}
MSE1 <- mean((IncomeQ1$logmove - m1) ^ 2)
MSE2 <- mean((IncomeQ2$logmove - m2) ^ 2)
MSE3 <- mean((IncomeQ3$logmove -m3) ^ 2)
MSE4 <- mean((IncomeQ4$logmove - m4) ^ 2)

MSE1
MSE2
MSE3
MSE4

```

#Quartile 3 has the lowest MSE
#Quartile 1 has the highest MSE 
