---
title: "HW6"
author: "Soham Ghose"
date: "May 12, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(plyr)
library(tidyr)
#install.packages('plyr')
#install.packages('rpart')
#install.packages('maptree')
#install.packages('cluster')
library(rpart)
library(maptree)
```






```{r setup2, echo=TRUE}
OJ <- read.csv("oj.csv")
OJ$logp <- log(OJ$price)
OJ$Q <- exp(OJ$logmove)
Df1 <- ddply(OJ, c('store','week'),function(x) c(weighted_price = weighted.mean(x$price,x$Q)))
OJ <- merge(OJ, Df1)
dataToPass<-OJ[,c("weighted_price","AGE60","EDUC",
                  "ETHNIC","INCOME","HHLARGE","WORKWOM",
                  "HVAL150","SSTRDIST","SSTRVOL","CPDIST5","CPWVOL5", "store", 'week','logmove', 'price', 'logp', 'brand', 'feat')]
fit<-rpart(as.formula(weighted_price ~ AGE60 + EDUC + ETHNIC+ INCOME + HHLARGE + WORKWOM
                 + HVAL150 + SSTRDIST + SSTRVOL + CPDIST5 + CPWVOL5) ,data=dataToPass,method="anova",cp=0.007)
draw.tree(fit) 

dataToPass$leaf = fit$where 
OJFinal <- dataToPass
draw.tree(fit) 

```

```{r setup3, echo=TRUE}
oj_leaf1 <- dataToPass %>% filter(leaf == 2)
oj_leaf2 <- dataToPass %>% filter(leaf == 4)
oj_leaf3 <- dataToPass %>% filter(leaf == 5)

reg_int1 <- glm(logmove~log(price)*brand*feat, data=oj_leaf1)
reg_int2 <- glm(logmove~log(price)*brand*feat, data=oj_leaf2)
reg_int3 <- glm(logmove~log(price)*brand*feat, data=oj_leaf3)

OJnew <- OJFinal %>%  select( brand , store , logp, week) %>% 
  spread(brand, logp) 

Df3 <- OJFinal %>% select(brand, store, logmove, week , logp, feat, INCOME, EDUC, AGE60, WORKWOM, ETHNIC, leaf)

OJ2 <- full_join(OJnew , Df3, by = c("store","week")) 

```

```{r ped, echo= TRUE}
#leaf 1 elasticities 
oj_leaf1_e <- OJ2 %>% filter(leaf == 2)
dom1 <- oj_leaf1_e %>% filter(brand == 'dominicks')
trop1 <- oj_leaf1_e %>% filter(brand == 'tropicana')
mm1 <- oj_leaf1_e %>% filter(brand == 'minute.maid')

dominicksreg1 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = dom1)
summary(dominicksreg1)

tropicanareg1 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = trop1)
summary(tropicanareg1)

minutemaidreg1 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = mm1)
summary(minutemaidreg1)

elasticities1 <- matrix(1:9, nrow = 3)
rownames(elasticities1) <- c("tropicana","minutemaid","dominicks")
colnames(elasticities1) <- c("PED_tropicana", "PED_MinuteMaid", "PED_dominicks")

elasticities1[1,1] <- coef(tropicanareg1)["tropicana"]
elasticities1[1,2] <- coef(tropicanareg1)["minute.maid"]
elasticities1[1,3] <- coef(tropicanareg1)["dominicks"]
elasticities1[2,1] <- coef(minutemaidreg1)["tropicana"]
elasticities1[2,2] <- coef(minutemaidreg1)["minute.maid"]
elasticities1[2,3] <- coef(minutemaidreg1)["dominicks"]
elasticities1[3,1] <- coef(dominicksreg1)["tropicana"]
elasticities1[3,2] <- coef(dominicksreg1)["minute.maid"]
elasticities1[3,3] <- coef(dominicksreg1)["dominicks"]
elasticities1
#leaf 2 elasticities 
oj_leaf2_e <- OJ2 %>% filter(leaf == 4)
dom2 <- oj_leaf2_e %>% filter(brand == 'dominicks')
trop2 <- oj_leaf2_e %>% filter(brand == 'tropicana')
mm2 <- oj_leaf2_e %>% filter(brand == 'minute.maid')

dominicksreg2 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = dom2)
summary(dominicksreg2)

tropicanareg2 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = trop2)
summary(tropicanareg2)

minutemaidreg2 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = mm2)
summary(minutemaidreg2)

elasticities2 <- matrix(1:9, nrow = 3)
rownames(elasticities2) <- c("tropicana","minutemaid","dominicks")
colnames(elasticities2) <- c("PED_tropicana", "PED_MinuteMaid", "PED_dominicks")

elasticities2[1,1] <- coef(tropicanareg2)["tropicana"]
elasticities2[1,2] <- coef(tropicanareg2)["minute.maid"]
elasticities2[1,3] <- coef(tropicanareg2)["dominicks"]
elasticities2[2,1] <- coef(minutemaidreg2)["tropicana"]
elasticities2[2,2] <- coef(minutemaidreg2)["minute.maid"]
elasticities2[2,3] <- coef(minutemaidreg2)["dominicks"]
elasticities2[3,1] <- coef(dominicksreg2)["tropicana"]
elasticities2[3,2] <- coef(dominicksreg2)["minute.maid"]
elasticities2[3,3] <- coef(dominicksreg2)["dominicks"]
elasticities2
#leaf 3 elasticities 

oj_leaf3_e <- OJ2 %>% filter(leaf == 5)
dom3 <- oj_leaf3_e %>% filter(brand == 'dominicks')
trop3 <- oj_leaf3_e %>% filter(brand == 'tropicana')
mm3 <- oj_leaf3_e %>% filter(brand == 'minute.maid')

dominicksreg3 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = dom3)
summary(dominicksreg3)

tropicanareg3 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = trop3)
summary(tropicanareg3)

minutemaidreg3 <- lm(logmove ~ (dominicks) + (minute.maid) + (tropicana) + INCOME + EDUC + AGE60 + WORKWOM + ETHNIC , data = mm3)
summary(minutemaidreg3)

elasticities3 <- matrix(1:9, nrow = 3)
rownames(elasticities3) <- c("tropicana","minutemaid","dominicks")
colnames(elasticities3) <- c("PED_tropicana", "PED_MinuteMaid", "PED_dominicks")

elasticities3[1,1] <- coef(tropicanareg3)["tropicana"]
elasticities3[1,2] <- coef(tropicanareg3)["minute.maid"]
elasticities3[1,3] <- coef(tropicanareg3)["dominicks"]
elasticities3[2,1] <- coef(minutemaidreg3)["tropicana"]
elasticities3[2,2] <- coef(minutemaidreg3)["minute.maid"]
elasticities3[2,3] <- coef(minutemaidreg3)["dominicks"]
elasticities3[3,1] <- coef(dominicksreg3)["tropicana"]
elasticities3[3,2] <- coef(dominicksreg3)["minute.maid"]
elasticities3[3,3] <- coef(dominicksreg3)["dominicks"]
elasticities3
```
4.	Now let's use the elasticities to think about pricing differentials.  
a.	In the leaf with the highest own-price elasticities, what should the markups be relative to the other leafs?  

The markups should be the lowest. 

b.	How do cross-price elasticities vary with the highest versus lowest own price elasticity leafs?  

i.	What does this imply about differences in markups within high versus low elasticity stores across brands?

Stores of a brand with the higher elasticities will have lower markups than stores with low elasticities. 

ii.	Can you say anything about what this means for the timing of sales?  Should they occur at the same or different times across stores?

They should occur at different times. 
